---
title: "BreastCancer"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Dữ liệu được lấy từ trang https://archive.ics.uci.edu/ml/machine-learning-databases/breast-cancer-wisconsin/

Citation Request:
   This breast cancer databases was obtained from the University of Wisconsin
   Hospitals, Madison from Dr. William H. Wolberg.  If you publish results
   when using this database, then please include this information in your
   acknowledgements.  Also, please cite one or more of:

   1. O. L. Mangasarian and W. H. Wolberg: "Cancer diagnosis via linear 
      programming", SIAM News, Volume 23, Number 5, September 1990, pp 1 & 18.

   2. William H. Wolberg and O.L. Mangasarian: "Multisurface method of 
      pattern separation for medical diagnosis applied to breast cytology", 
      Proceedings of the National Academy of Sciences, U.S.A., Volume 87, 
      December 1990, pp 9193-9196.

   3. O. L. Mangasarian, R. Setiono, and W.H. Wolberg: "Pattern recognition 
      via linear programming: Theory and application to medical diagnosis", 
      in: "Large-scale numerical optimization", Thomas F. Coleman and Yuying
      Li, editors, SIAM Publications, Philadelphia 1990, pp 22-30.

   4. K. P. Bennett & O. L. Mangasarian: "Robust linear programming 
      discrimination of two linearly inseparable sets", Optimization Methods
      and Software 1, 1992, 23-34 (Gordon & Breach Science Publishers).
      
  Có 699 dòng (đối tượng) và 11 thuộc tính.
  Thiếu 16 giá trị thuộc tính.
  Có 2 loại lành và ác tính. 
  #  Attribute                                                   Domain
   -- ------------------------------------------------------------------
   1. Sample code number(Sample_No)                              id number
   2. Clump Thickness (Clump_Thickness)                          1 - 10
   3. Uniformity of Cell Size(Uniformity_Cell_Size)              1 - 10
   4. Uniformity of Cell Shape(Uniformity_Cell_Shape)            1 - 10
   5. Marginal Adhesion(Marginal_Adhesion)                       1 - 10
   6. Single Epithelial Cell Size(Single_Epithelial_Cell_Size)   1 - 10
   7. Bare Nuclei(Bare_Nuclei)                                   1 - 10
   8. Bland Chromatin(Bland_Chromatin)                           1 - 10
   9. Normal Nucleoli(Normal_Nucleoli)                           1 - 10
  10. Mitoses(Mitoses)                                           1 - 10
  11. Class:(class)                                             (2 for benign, 4 for malignant)
  

**Đọc dữ liệu**
```{r read_data}
#Ctrl+Shift+H để chọn directory chứa folder data
data_path <- file.path( "/data", "breast-cancer-wisconsin.data")

names <- c('Sample_No', 'Clump_Thickness', 'Uniformity_Cell_Size', 
         'Uniformity_Cell_Shape', 'Marginal_Adhesion', 'Single_Epithelial_Cell_Size', 
         'Bare_Nuclei', 'Bland_Chromatin', 
         'Normal_Nucleoli','Mitoses', 
         'class')

data <- read.table(data_path, sep = ',', col.names = names)
#"D:/University/3_2/datamining/project/DataMining_BreastCancer/BreastCancer/data/breast-cancer-wisconsin.data"
OutCome=ifelse(data$class==2,"No","Yes")

data=data.frame(data,OutCome)

#drop class and sample_no column
data$class<-NULL
data$Sample_No<-NULL

data$OutCome<-as.factor(data$OutCome)

```
**Xem dữ liệu thô**
```{r head}
head(data,5)
```
```{r str}
str(data)
```
```{r summary}
summary(data)
```

```{r column name}
names(data)
```
```{r datatype}
class(data)
```
```{r checkNa}
sum(is.na(data))
```

```{r}
table(data$OutCome)/nrow(data)
``` 
Có 65% lành tính( benign) và 37% ác tính trong số các bệnh nhân được chẩn đoán trong tập dataset.


*Building model*


```{r eval=FALSE}
#install.packages("randomForest")
```

```{r library}
library(randomForest)
```

```{r model}

rf_model <- randomForest(OutCome ~ ., data=data, ntree=1500, mtry=3, importance=TRUE)
rf_model
```
Số cây : 1500
Số biến được thử ở mỗi lần tách : 3
Loại random forest: phân loại
OOB estimate tỉ lệ lỗi : 3 %


```{r plotmodel}
plot(rf_model)

```
Biểu đồ lỗi cho biết lỗi với các lớp khác nhau ( màu đỏ và xanh) và out-of-bag so với số lượng cây. Màu đỏ lành tính và mày xanh ác tính. Lỗi thấp nhất đạt được từ 1200, sau đó điều chỉnh cũng không cải thiện hiệu suất.


**chia tập dữ liệu thành tập training và testing**
chia dữ liệu 70% train và 30% test
```{r installLibrary eval=false}
#install.packages("caTools")
```

```{r splitdata}
set.seed(2)
library(caTools)
sample<-sample.split(data$OutCome, SplitRatio=0.70)

data.train<- subset(data,sample==TRUE)

data.test<-subset(data,sample==FALSE)
```
**Model building & Interpretation on Training and Testing Data**

```{r program1}
r_model<-randomForest(OutCome~., data=data.train, ntree=1500, mtry=3, importance=TRUE)

print(r_model)
```
OOB error or prediction error : 4.49%

```{r program1}
plot(r_model)
```

```{r program1}
plot(margin(r_model, data.test$OutCome))
```