---
title: "BreastCancer"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# instruction data

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

Dữ liệu được lấy từ trang https://archive.ics.uci.edu/ml/machine-learning-databases/breast-cancer-wisconsin/

Citation Request:
   This breast cancer databases was obtained from the University of Wisconsin
   Hospitals, Madison from Dr. William H. Wolberg.  If you publish results
   when using this database, then please include this information in your
   acknowledgements.  Also, please cite one or more of:

   1. O. L. Mangasarian and W. H. Wolberg: "Cancer diagnosis via linear 
      programming", SIAM News, Volume 23, Number 5, September 1990, pp 1 & 18.

   2. William H. Wolberg and O.L. Mangasarian: "Multisurface method of 
      pattern separation for medical diagnosis applied to breast cytology", 
      Proceedings of the National Academy of Sciences, U.S.A., Volume 87, 
      December 1990, pp 9193-9196.

   3. O. L. Mangasarian, R. Setiono, and W.H. Wolberg: "Pattern recognition 
      via linear programming: Theory and application to medical diagnosis", 
      in: "Large-scale numerical optimization", Thomas F. Coleman and Yuying
      Li, editors, SIAM Publications, Philadelphia 1990, pp 22-30.

   4. K. P. Bennett & O. L. Mangasarian: "Robust linear programming 
      discrimination of two linearly inseparable sets", Optimization Methods
      and Software 1, 1992, 23-34 (Gordon & Breach Science Publishers).
      
  Có 699 dòng (đối tượng) và 11 thuộc tính.
  Thiếu 16 giá trị thuộc tính.
  Có 2 loại lành và ác tính. 
  #  Attribute                                                   Domain
   -- ------------------------------------------------------------------
   1. Sample code number(Sample_No)                              id number
   2. Clump Thickness (Clump_Thickness)                          1 - 10
   3. Uniformity of Cell Size(Uniformity_Cell_Size)              1 - 10
   4. Uniformity of Cell Shape(Uniformity_Cell_Shape)            1 - 10
   5. Marginal Adhesion(Marginal_Adhesion)                       1 - 10
   6. Single Epithelial Cell Size(Single_Epithelial_Cell_Size)   1 - 10
   7. Bare Nuclei(Bare_Nuclei)                                   1 - 10
   8. Bland Chromatin(Bland_Chromatin)                           1 - 10
   9. Normal Nucleoli(Normal_Nucleoli)                           1 - 10
  10. Mitoses(Mitoses)                                           1 - 10
  11. Class:(class)                                             (2 for benign, 4 for malignant)
  

**Đọc dữ liệu**
```{r read_data}
names <- c('Sample_No', 'Clump_Thickness', 'Uniformity_Cell_Size', 
         'Uniformity_Cell_Shape', 'Marginal_Adhesion', 'Single_Epithelial_Cell_Size', 
         'Bare_Nuclei', 'Bland_Chromatin', 
         'Normal_Nucleoli','Mitoses', 
         'class')
data_set <- read.table("E:/Nam3_KyII/Data mining/DoAn/DataMining_BreastCancer/BreastCancer/data/breast-cancer-wisconsin.data", sep = ',', col.names = names)

data_set<-data.frame(data_set)

data_set<-data_set[data_set$Bare_Nuclei != "?",]
data_set$Bare_Nuclei<-as.numeric(data_set$Bare_Nuclei)

Benign<-ifelse(data_set$class==2,"Yes","No")

data_set<-data.frame(data_set,Benign)

#drop class and sample_no column
data_set$class<-NULL
data_set$Sample_No<-NULL
data_set
```
**Xem dữ liệu thô**
```{r head}
head(data_set,5)
str(data_set)
summary(data_set)
```
```{r }
library(rpart)
library(rpart.plot)
#set.seed(123)
num <- nrow(data_set)
train_index = sample(num, size = trunc(0.85 * num))
train_data = data_set[train_index, ]
test_data = data_set[-train_index, ]



model.full<- rpart(Benign ~., data = train_data, method = "class")
model.full
prp(model.full)
rpart.plot(model.full, extra = 100)


Predict <- predict(model.full, test_data, type = "class")
Predict


Confusion_matrix <- table(Predict,test_data$Benign)
print(Confusion_matrix)

Error_rate=1-(Confusion_matrix[1,1]+Confusion_matrix[2,2])/sum(Confusion_matrix)
Error_rate
```


```{r }
library(glmnet)
library(Matrix)
library(lattice)
library(ellipsis)
library(ggplot2)
library(gower)
library(caret)
library(rpart)
library(rpart.plot)


model.tree<- train(Benign ~., data = data_set, method="rpart", trControl=trainControl(method = "cv"))
model.tree
rpart.plot(model.tree$finalModel, extra = 104, nn = TRUE)

Predict<-predict(model.tree$finalModel, test_data, type = "class")
Predict

Confusion_matrix <- table(Predict,test_data$Benign)
print(Confusion_matrix)

Error_rate=1-(Confusion_matrix[1,1]+Confusion_matrix[2,2])/sum(Confusion_matrix)
Error_rate

```